\chapter*{General Conclusion and Perspectives}
\addcontentsline{toc}{chapter}{General Conclusion and Perspectives}
\markboth{General Conclusion and Perspectives}{General Conclusion and Perspectives}

This internship marked a significant step in my academic and professional journey, consolidating
theoretical knowledge through practical work on a distributed microservices architecture with AI
integration. Developing the BVIRAL platform was an enriching experience that allowed me to
strengthen my skills with technologies such as FastAPI, Next.js, OpenSearch, Qdrant, and Docker.

Future evolution prospects for the project include:
\begin{itemize}
  \item \textbf{Multimodal video embedding pipeline}: Indexing thumbnails and transcripts with
    richer embeddings to enable scene-level semantic search.
  \item \textbf{LLM evaluation harness}: Building an offline evaluation suite to track RAG
    relevance, classifier accuracy, and hallucination rate across releases.
  \item \textbf{Deployment on Kubernetes}: Migrating from the current setup to Kubernetes for
    auto-scaling, stronger resilience, and high availability.
  \item \textbf{Advanced analytics dashboard}: Extending the admin dashboard with deeper usage,
    operational, and recommendation insights.
\end{itemize}

In summary, this internship concludes my university studies and fully prepares me to enter the
professional world. It has strengthened my software development skills and given me a solid
foundation to face future computer engineering challenges.
