\chapter*{Webography}
\markboth{Webography}{Webography}
\addcontentsline{toc}{chapter}{Webography}
\label{chap:webographie}
\pagestyle{empty}

The following web resources were consulted while writing this report, especially for presenting
the host organization, analyzing existing solutions, describing the technologies and tools used,
and documenting design and architecture choices.

\begin{enumerate}[leftmargin=0pt]

  \item \label{web:bviral} \textbf{BVIRAL Media Inc.} :
        \url{https://www.bviral.com/} (Accessed on January 15, 2026).\\
        Official website used to present the host organization and describe the viral video
        content licensing business model (Chapter~1, Section~1.1).

  \item \label{web:getty} \textbf{Getty Images} :
        \url{https://www.gettyimages.com/} (Accessed on January 20, 2026).\\
        Platform analyzed in the comparative study of existing video rights management and semantic
        search solutions (Chapter~1, Section~1.3).

  \item \label{web:storyful} \textbf{Storyful} :
        \url{https://storyful.com/} (Accessed on January 20, 2026).\\
        Social media monitoring platform analyzed as part of the state-of-the-art review, with a
        focus on manual licensing workflows (Chapter~1, Section~1.3).

  \item \label{web:jukin} \textbf{Jukin Media} :
        \url{https://www.jukinmedia.com/} (Accessed on January 21, 2026).\\
        Curated subscription-based video catalog solution analyzed in the comparative study
        (Chapter~1, Section~1.3).

  \item \label{web:shutterstock} \textbf{Shutterstock Video} :
        \url{https://www.shutterstock.com/video} (Accessed on January 21, 2026).\\
        International platform with semantic and filtered search analyzed for feature comparison
        (Chapter~1, Section~1.3).

  \item \label{web:scrumorg} \textbf{Scrum.org --- The Scrum Guide} :
        \url{https://www.scrum.org/resources/scrum-guide} (Accessed on January 25, 2026).\\
        Main reference for describing the Agile Scrum methodology and sprint process used in the
        project (Chapter~1, Section~1.4).

  \item \label{web:fastapi} \textbf{FastAPI} :
        \url{https://fastapi.tiangolo.com} (Accessed on February 1, 2026).\\
        Python framework used for AR-API and Agentic Helper.

  \item \label{web:flask} \textbf{Flask} :
        \url{https://flask.palletsprojects.com} (Accessed on February 1, 2026).\\
        Python framework used for the Videos Search API.

  \item \label{web:nextjs} \textbf{Next.js} :
        \url{https://nextjs.org/docs} (Accessed on February 2, 2026).\\
        React framework used for both portals and BFF routes (Chapters~2 and~7).

  \item \label{web:sqlalchemy} \textbf{SQLAlchemy} :
        \url{https://docs.sqlalchemy.org} (Accessed on February 3, 2026).\\
        Async Python ORM used for PostgreSQL access in FastAPI services.

  \item \label{web:alembic} \textbf{Alembic} :
        \url{https://alembic.sqlalchemy.org} (Accessed on February 3, 2026).\\
        Database migration tool used for AR-API schema evolution.

  \item \label{web:pydantic} \textbf{Pydantic} :
        \url{https://docs.pydantic.dev} (Accessed on February 4, 2026).\\
        Data validation library used for strict schemas and structured LLM outputs.

  \item \label{web:celery} \textbf{Celery} :
        \url{https://docs.celeryq.dev} (Accessed on February 5, 2026).\\
        Distributed task queue used for notifications and background processing.

  \item \label{web:radixui} \textbf{Radix UI} :
        \url{https://www.radix-ui.com} (Accessed on February 6, 2026).\\
        UI primitives used with Tailwind CSS in the Video Search Portal.

  \item \label{web:mui} \textbf{Material UI (MUI)} :
        \url{https://mui.com/material-ui/} (Accessed on February 6, 2026).\\
        UI component library used for dashboards and admin interfaces.

  \item \label{web:tailwind} \textbf{Tailwind CSS} :
        \url{https://tailwindcss.com/docs} (Accessed on February 6, 2026).\\
        Utility-first CSS framework used in the Video Search Portal.

  \item \label{web:langchain} \textbf{LangChain} :
        \url{https://python.langchain.com/docs/} (Accessed on February 10, 2026).\\
        LLM orchestration framework used for prompt chains and RAG.

  \item \label{web:langgraph} \textbf{LangGraph} :
        \url{https://langchain-ai.github.io/langgraph/} (Accessed on February 10, 2026).\\
        State-graph framework used for the video search ReAct agent.

  \item \label{web:langsmith} \textbf{LangSmith} :
        \url{https://smith.langchain.com/} (Accessed on February 11, 2026).\\
        Tracing and prompt management platform for Agentic Helper.

  \item \label{web:openai} \textbf{OpenAI API} :
        \url{https://platform.openai.com/docs/} (Accessed on February 12, 2026).\\
        API used for GPT models, embeddings, and Whisper transcription.

  \item \label{web:qdrant} \textbf{Qdrant} :
        \url{https://qdrant.tech/documentation/} (Accessed on February 14, 2026).\\
        Vector database used to store and retrieve semantic embeddings.

  \item \label{web:opensearch} \textbf{OpenSearch} :
        \url{https://opensearch.org/docs/} (Accessed on February 15, 2026).\\
        Search engine used for lexical, vector, and faceted video search.

  \item \label{web:clerk} \textbf{Clerk} :
        \url{https://clerk.com/docs} (Accessed on February 18, 2026).\\
        Authentication and user management service used across portals and AR-API.

  \item \label{web:stripe} \textbf{Stripe} :
        \url{https://stripe.com/docs} (Accessed on February 19, 2026).\\
        Payment platform used for checkout, subscriptions, and billing flows.

  \item \label{web:slack_api} \textbf{Slack Block Kit} :
        \url{https://api.slack.com/block-kit} (Accessed on February 20, 2026).\\
        Slack API used for structured notifications in backend workflows.

  \item \label{web:redis} \textbf{Redis} :
        \url{https://redis.io/docs/} (Accessed on February 22, 2026).\\
        In-memory data store used as Celery broker and state cache.

  \item \label{web:postgresql} \textbf{PostgreSQL} :
        \url{https://www.postgresql.org/docs/} (Accessed on February 22, 2026).\\
        Relational database used for core AR-API domain data.

  \item \label{web:docker} \textbf{Docker} :
        \url{https://docs.docker.com/} (Accessed on February 25, 2026).\\
        Containerization platform used to package services.

  \item \label{web:dockercompose} \textbf{Docker Compose} :
        \url{https://docs.docker.com/compose/} (Accessed on February 25, 2026).\\
        Local orchestration tool used to run the full stack.

  \item \label{web:python} \textbf{Python} :
        \url{https://docs.python.org/3/} (Accessed on March 2, 2026).\\
        Main backend language used in AR-API, Agentic Helper, and Videos Search API.

  \item \label{web:typescript} \textbf{TypeScript} :
        \url{https://www.typescriptlang.org/docs/} (Accessed on March 2, 2026).\\
        Main frontend language used in both Next.js portals.

  \item \label{web:postman} \textbf{Postman} :
        \url{https://www.postman.com/product/api-client/} (Accessed on March 4, 2026).\\
        API client used to test backend endpoints.

  \item \label{web:cursor} \textbf{Cursor IDE} :
        \url{https://www.cursor.com/} (Accessed on March 4, 2026).\\
        Primary AI-assisted code editor used during development.

  \item \label{web:vscode} \textbf{Visual Studio Code} :
        \url{https://code.visualstudio.com/docs} (Accessed on March 5, 2026).\\
        Secondary code editor used alongside Cursor IDE.

  \item \label{web:qdrant_cloud_console} \textbf{Qdrant Cloud Console} :
        \url{https://cloud.qdrant.io/} (Accessed on March 6, 2026).\\
        Web interface used to inspect and manage vector collections.

  \item \label{web:opensearch_dashboards} \textbf{OpenSearch Dashboards} :
        \url{https://opensearch.org/docs/latest/dashboards/} (Accessed on March 6, 2026).\\
        Visualization interface used to inspect OpenSearch indexes and queries.

  \item \label{web:pytest} \textbf{pytest} :
        \url{https://docs.pytest.org/} (Accessed on March 8, 2026).\\
        Python testing framework used for backend test suites.

\end{enumerate}
